\chapter{Introduction\label{chap:introduction}}

Each chapter heading is typeset in this way --- this in an integral
part of the style, so if you don't like it abdnthesis.cls may not be
for you. However, do feel free to modify the .cls file to your needs.

\section{Defaults}

\begin{itemize}
\item oneside --- assuming single sided printing.

\item onecolumn --- \LaTeX\ will give you an error if you try to use
  the twocolumn option, not that anyone would contemplate this for a
  thesis.

\item 11pt --- this works best with the text height and width on A4
  paper.

\item 1.5 line spacing --- looks much better than double spacing.

\item Times Roman font --- for both text and maths with the exception
  of mathcal, but see below for options.
\end{itemize}

\section{Options}

\begin{itemize}

\item These are mutually exclusive options that are used to specify
 the type of degree that the thesis is to be submitted in partial
 fulfilment of the requirements of:

\begin{itemize}
\item phd or PhD -- the default.
\item mphil or MPhil -- for Master of Philosophy Theses.
\item msc or MSc -- for MSc project reports.
\item bsc or BSc -- for BSc project reports.
\end{itemize}

\item Two self-explanatory options for changing the line spacing from
 the default 1.5.

\begin{itemize}
\item singlespace
\item doublespace
\end{itemize}

\item titlebox --- this option ensures that the title of the document
 fits within the window on the standard departmental BSc or MSc
 project report front cover.
 
\item twoside --- this option is if you wish to print your thesis
  using a double sided printer.  Note that the University regulations 
  do not permit the submission of theses printed double sided.

\item cmmath --- this action changes the font used in math mode to be
  Computer Modern. The default is for all math mode fonts to be times
  with the exception of the mathcal font. If you want to also use
  times for mathcal, you need to comment out these two lines in the
  abdnthesis.cls file:
\begin{verbatim}
        \SetMathAlphabet{\mathcal}{normal}{OMS}{cmsy}{m}{n}
        \SetMathAlphabet{\mathcal}{bold}{OMS}{cmsy}{b}{n}
\end{verbatim}

\item cmall --- if you want to go with Computer Modern for both
  text and maths, use this option.
\end{itemize}

There is also an \emph{optional} command for including prior
qualifications within the title page; some like to do this. Prior to
version 2.3 (2013/08/11) \LaTeX\ would give an error if this was not
declared, even if you didn't want this information on the title
page. This meant that you would have to have made the declaration
\verb+\qualifications{}+, which was an ugly solution. Now, ``empty''
declaration can simply be omitted.



